Automated Synthesis of State-Space Digital Systems

### 2016-12-21 cav2017/cav2017.tex
Added comments to Preliminaries

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u},\nonumber
\end{align}
which are soundly discretized (as shown in the appendix) into 
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers in the form
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k.
\end{equation}
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\mat{B} \in \mathcal{G}_B.
\end{align*}

>>>>

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u},\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, 
$\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a digital system. Eq.~\ref{eq:ode} is soundly discretized 
(as shown in the appendix) into 
\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers in the form
\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k.
\end{equation}
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\mat{B} \in \mathcal{G}_B.
\end{align*}
